%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-red}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
%\photo[circle,noedge,left]{./examples/profile}
\name{Dave}{Scott}
\position{Machine Learning Engineer{\enskip\cdotp\enskip}Data Scientist}
\address{Edmonton, Alberta, Canada}

\mobile{(+1) 780-964-8078}
\email{davejscott@shaw.ca}
%\homepage{www.posquit0.com}
\github{davejscott}
\linkedin{davejscott}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
\medium{davejscott}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \medium{madium-id}
% \googlescholar{googlescholar-id}{name-to-display}
%% \firstname and \lastname will be used
% \googlescholar{googlescholar-id}{}
% \extrainfo{extra informations}

%\quote{``Be the change that you want to see in the world."}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {Company Recruitment Team}
  {Google Inc.\\1600 Amphitheatre Parkway\\Mountain View, CA 94043}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application for Machine Learning Engineer}
% How the letter is opened
\letteropening{Dear Tracy Parks}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
\letterenclosure[Attached]{Resume}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Dave Scott~~~·~~~Cover Letter}
  {}

% Print the title with above letter informations
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

\lettersection{About Me}
Canadian born and raised, with a growth mindset and an eagerness to learn has shaped me into the Machine Learning Engineer I am today. A curiosity to innovate and design paired with a strong work ethic has separated me from my peers as a disciplined, quick learner, coupled with elite soft skills. Backed with a strong knowledge of machine learning algorithm development and a curiosity to learn, I design, develop, program, and implement machine learning algorithms for time series applications.

\lettersection{Why Google?}
As a child, I fell in love with Google and it's mission to freely share information to the masses. Utilizing Google and Youtube helped me develop strong self-teaching abilities, as well as the capability to build businesses. Being eager to solve my ideas harnessing complex information at a young age that were not available to be taught in school, Google and its products helped me. As Google continues to evolve its business units to include more applications and products, I am excited, much like I was as a child, at the possibilities available for Machine Learning Engineers to influence our next generation of youth.

\lettersection{Why Me?}
Coming from a "non-traditional" background as a Machine Learning Engineer, I harnessed my diversity to become an expert in Program Management, creating effective solutions for industrial automation and IT problems. Over the course of my Master's in Computer Process Control Engineering, I gained a strong familiarity in software development and coding, winning 3 International Hackathons, as well as having a 6 month-exchange at the MIT of China, Tsinghua University. While at Tsinghua University, I published one research paper, on a novel machine learning algorithm, and went from having no background in Chinese to being an Intermediate Chinese Speaker and writing my HSK 3 exam in 5 months of studying; demonstrating my ability to quickly absorb, learn, and apply information.

\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter informations
\makeletterclosing

\end{document}
