%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------

\cventry
{Incoming Founder in Residence} % Job title
{Entrepreneur First} % Organization
{Singapore} % Location
{Oct. 2019 - Current} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Selected as one of 50 co-founders from across the world to participate in Entrepreneur First's 7th Cohort in Singapore.}  
		\item {Entrepreneur First is a deep-tech incubator where high-tech companies are built, backed by the founders of LinkedIn, DeepMind, and Paypal.}    
	\end{cvitems}
}

%---------------------------------------------------------
\cventry
{Machine Learning Research Engineer - Master's Exchange} % Job title
{Tsinghua University} % Organization
{Beijing, China} % Location
{Feb. 2019 - Aug. 2019} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Developed a first-of-its-kind ML algorithm that monitors and detects faults during industrial process monitoring.}
		\item {Implemented algorithm with industrial processes (MATLAB, Python), identifying faults 20\% faster and raising 35\% less false alarms than other leading ML algorithms.}
	\end{cvitems}
}

%---------------------------------------------------------
\cventry
{Industrial Automation \& Machine Learning Research Engineer} % Job title
{University of Alberta} % Organization
{Edmonton, Canada} % Location
{Sep. 2018 - Feb. 2019} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Re-engineered Pump Fault Analysis Software (Python) by designing a UI for end-user to interact with software and distinguish faults.}   
	\end{cvitems}
}

%---------------------------------------------------------
\cventry
{Data Analytics Field Engineer, Intern} % Job title
{Schlumberger Limited} % Organization
{Tulsa, USA} % Location
{Jun. 2018 - Jul. 2018} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Developed ML application that ensured efficient operations by utilizing real-time vibration and GPS data to detect 10 drilling faults.}
		\item {Formulated and launched IoT program that connected microprocessors to satellites, improving IoT links and saving \$100,000 USD in lost time.}
	\end{cvitems}
}

%---------------------------------------------------------
\cventry
{Data Science \& Controls Engineer, Co-op Student} % Job title
{Canadian Natural Resources Limited} % Organization
{Calgary, Canada} % Location
{May. 2016 - Dec. 2016} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Forecasted and modeled capital expenditures of 80 capital projects into models and graphs (R), delivering KPIs to senior management.}
	\end{cvitems}
}


%---------------------------------------------------------
 % \cventry
 %   {Process Engineer, Co-op Student} % Job title
  %  {Canadian Natural Resources Limited} % Organization
  %  {Fort McMurray, Canada} % Location
  %  {Jan. 2015 - Aug. 2015} % Date(s)
  %  {
   %   \begin{cvitems} % Description(s) of tasks/responsibilities
    %    \item {Optimized the operation of a 125,000 bbl. /d synthetic crude oil upgrader by creating data analytics tools to detect process faults.}
     %   \item {Resolved savings of chemicals by over 25\% by creating a cross-validation algorithm streamlining data transfer utilizing SQL from PI Datalink, saving CNRL over \$400,000 CAD a year.}
    %  end{cvitems}
  %  }

\end{cventries}
