%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Machine Learning Engineer - Master's Exchange} % Job title
    {Tsinghua University} % Organization
    {Beijing, China} % Location
    {Feb. 2019 - Current} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Solved a previously-unsolved data science problem by developing a robust signal-processing Machine Learning algorithm (MATLAB, Python), with direct industrial applications for over >5 industries.}
        \item {Derived a novel statistics formulation for non-stationary and stationary process data that identified and detected faults 20\% faster and raised 35\% less false alarms than the PCA, CVA, and PLS multivariate statistical process monitoring methods.}
        \item {Built fully automated modelling and monitoring pipelines (Scikit-learn, Tensorflow, MATLAB) for industrial process data including backpropagation algorithms and intelligent model initialization.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Computer \& Machine Learning Research Engineer} % Job title
    {University of Alberta} % Organization
    {Edmonton, Canada} % Location
    {Sep. 2017 - Feb. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed fault detection software to analyse pump faults, creating a simple GUI interface for end-user to interact with the software.}
        \item {Managed a client project to implement data mining and machine learning pipeline (KnowledgeNet Analytics, C++) for a Cloud Control System that contained over 5000+ process variables.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Data Analytics Field Engineer, Intern} % Job title
    {Schlumberger Limited} % Organization
    {Tulsa, USA \& Calgary, Canada} % Location
    {Jun. 2018 - Jul. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Analysed process data from drilling measurement tools to detect 10 drilling faults and provided adjustments for engineers, decreasing the required time for the drilling operation.}
        \item {Diagnosed and designed IoT disconnections, delivering solutions for inefficiencies and saving the client over \$150,000 USD in lost time, while enhancing site communication and safety.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Data Science \& Controls Engineer, Co-op Student} % Job title
    {Canadian Natural Resources Limited} % Organization
    {Calgary, Canada} % Location
    {Jan. 2013 - Feb. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Forecasted and modelled project progress of 80 capital projects into economic models and graphs (RStudio) to deliver key performance indicators for projects to senior management.}
        \item {Created automated reporting and analytics software, reducing required time to upload project updates for project managers by over 30\% (VBA).}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {ShitOne Corp.} % Organization
    {Seoul, S.Korea} % Location
    {Dec. 2011 - Feb. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a proxy drive smartphone application which connects proxy driver and customer.}
        \item {Implemented overall Android application logic and wrote API server for community service, along with lead engineer who designed bidding protocol on raw socket and implemented API server for bidding.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Freelance Penetration Tester} % Job title
    {SAMSUNG Electronics} % Organization
    {S.Korea} % Location
    {Sep. 2013, Mar. 2011 - Oct. 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Conducted penetration testing on SAMSUNG KNOX, which is solution for enterprise mobile security.}
        \item {Conducted penetration testing on SAMSUNG Smart TV.}
      \end{cvitems}
      %\begin{cvsubentries}
      %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
      %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
      %\end{cvsubentries}
    }

%---------------------------------------------------------
\end{cventries}
